Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-12-20 paper/intro.tex
Revise based on reviewer input and read

We have been developing the {\em BriefCASE} \oldjunk{toolsuite} toolkit to address this need.
\brfcs\ is a Model-Based Systems Engineering (MBSE) environment
built in the Open Source AADL\footnote{AADL is the acronym for
Architecture Analysis and Design Language~\cite{aadl}.}  Tool
Environment (OSATE) to add new capabilities for building
cyber-resilient systems. 
%
In this paper we describe how it facilitates specifying, testing,
verifying, and synthesizing high assurance components inserted into a
system to improve its cyber-resiliency.  The main organizing concept
is that of an architecture-to-architecture \emph{security-improving
transform}, achieved via the insertion of \oldjunk{a} new architectural
component\newjunk{s} aimed at mitigating \oldjunk{a} cyber-vulnerabilit\oldjunk{y}\newjunk{ies}.  We describe two
such transformations in this paper: (1) the insertion of a
filter to prevent malformed data from a malicious actor being
propagated to downstream components, and (2) the insertion of a
runtime monitor to detect (and alert) unexpected behaviors arising
from untrusted components.

@@

\newjunk{%
The contributions of this paper relate to the aspects of \brfcs\ concerning evidence that a high-assurance component meets its intended purpose and is properly implemented. 
%
We leverage the existing {\agr}\footnote{AGREE is the acronym for \emph{Assume Guarantee Reasoning Environment}.} model checker to provide evidence of the former and the existing verified \ckml\ compiler to provide evidence of the latter \cite{agree2013,compositional-analysis-agree,nfm:agree,cakeml}. 
%
Specifically, designers write \emph{contracts} to formally specify input and output properties of the system and its components, and \agr\ proves via model checking whether or not the system composition preserves contract requirements at component inputs and guarantees contract obligations at system outputs.
%
In this way, \agr\ provides the formal framework we use to describe the behavior of an inserted high-assurance component, such as a filter or monitor, and then prove if adding such a component to the system improves
cyber-resiliency.
}

>>>>

We have been developing the {\em BriefCASE} \oldjunk{toolsuite} toolkit to address this need.
\brfcs\ is a Model-Based Systems Engineering (MBSE) environment
built in the Open Source AADL\footnote{AADL is the acronym for
Architecture Analysis and Design Language~\cite{aadl}.}  Tool
Environment (OSATE) to add new capabilities for building
cyber-resilient systems. 
%
In this paper we describe how it facilitates specifying, testing,
verifying, and synthesizing high assurance components inserted into a
system to improve its cyber-resiliency.  The main organizing concept
is that of an architecture-to-architecture \emph{security-improving
transform}, achieved via the insertion of \oldjunk{a} new architectural
component\newjunk{s} aimed at mitigating \oldjunk{a} cyber-vulnerabilit\oldjunk{y}\newjunk{ies}.  We describe two
such transformations in this paper: (1) the insertion of a
filter to prevent malformed data from a malicious actor being
propagated to downstream components, and (2) the insertion of a
runtime monitor to detect (and alert) unexpected behaviors arising
from untrusted components. 
\newjunk{
We refer to these as \emph{high-assurance components} because they must be correct and fulfill their intended purpose for the system to be cyber-resilient.
}

@@

\newjunk{%
The contributions of this paper relate to the aspects of \brfcs\ concerning evidence that such high-assurance components meet their intended purpose and are properly implemented. 
%
We leverage the existing {\agr}\footnote{AGREE is the acronym for \emph{Assume Guarantee Reasoning Environment}.} model checker to provide evidence of the former and the existing verified \ckml\ compiler to provide evidence of the latter \cite{agree2013,compositional-analysis-agree,nfm:agree,cakeml}. 
%
Specifically, designers write \emph{contracts} to formally specify input and output properties of the system and its components, and \agr\ proves via model checking whether or not the system composition preserves contract requirements at component inputs and guarantees contract obligations at system outputs.
%
In this way, \agr\ provides the formal framework we use to describe the behavior of an inserted high-assurance component, such as a filter or monitor, and then prove if adding such a component to the system improves
cyber-resiliency.
}
